Challenges in Developing Great MCQMC Software

### 2022-07-13 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

		\item  \alert{Complete}---contain the components or have easy access to components in other libraries to solve real, complex problems

@@

		\item  \alert{Sustainable}--have a sufficient user base and developer community for updates and maintenance

		\item \alert{Scalable}--take advantage of latest computer architectures for speed and to tackle large problems

>>>>

		\item  \alert{Complete}---contain the components or  easily access components in other libraries to solve real, complex problems

@@

		\item  \alert{Sustainable}---have a sufficient user base and developer community for updates and maintenance

		\item \alert{Scalable}---take advantage of advanced computer architectures for speed and to solve large problems
